---
title: "SSOSurveyStudy"
author: "Ahmad R Pratama"
date: "7/30/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Preparation
## Packages
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(summarytools)
library(ggfortify)
library(lm.beta)
library(sjPlot)
library(gridExtra)
library(dplyr)
library(hrbrthemes)
library(ggalt)
library(ggtext)
library(ggpubr)
```
## Attach dataset
```{r, warning=FALSE, message=FALSE}
data <- read_csv("ssosurvey283.csv")
summary(data)
```
## Summary Statistics
```{r}
data
freq(data, report.nas = F)
```
### Dependent Variables
```{r}
dv <- data[, c('knowledge','k1','k2','k3','k4','k5','attitude','a1','a2','a3','a4','a5','behavior','b1','b2','b3','b4','b5','score')]
msd.dv <- dv %>% summarise_each(funs(mean, sd, min, max))
round(msd.dv,digits=2)
```


### Independent Variables
```{r}
iv <- data[, c('familiarity','f1','f2','f3','privacy','pr1','pr2','pr3','pr4','pr5','extraversion','agreeableness','conscientiousness','emotionalstability','openness')]
msd.iv <- iv %>% summarise_each(funs(mean, sd, min, max))
round(msd.iv,digits=2)
```

```{r}
mean(data$age)
sd(data$age)
```



## Data Visualization
### Scatterplot Age - Score
```{r}
g1 <- ggplot(data, aes(x=age, y=score, shape=gender, color=gender)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

g1 + facet_grid(rows = vars(roles))

g2 <- ggplot(data, aes(x=age, y=score, shape=roles, color=roles)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

g2 + facet_grid(rows = vars(gender))

g3 <- ggplot(data, aes(x=age, y=score, shape=gender, color=roles)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

g3 + facet_grid(vars(gender), vars(roles))+
   labs(title = "SSO Security Awareness by Age", x="Age (years old)", y="SSO Security Awareness Score")

g4 <- g3 + facet_grid(vars(gender), vars(roles))+
   labs(title = "SSO Security Awareness by Age", x="Age (years old)", y="SSO Security Awareness Score")
   
#g3 + facet_grid(vars(roles), vars(gender))

ggsave("fig2.pdf", plot= g4, dpi="print")
```
### Score by Gender
```{r}
scores <- data[,c('gender','score','knowledge','attitude','behavior')]
sg <- scores %>% 
    group_by(gender) %>%
      summarize_each(funs(mean))
sg
```
### Score by Roles
```{r}
scores <- data[,c('roles','score','knowledge','attitude','behavior')]
sg <- scores %>% 
    group_by(roles) %>%
      summarize_each(funs(mean))
sg
```
### Dumbbell Plots by Gender and Roles
```{r}
tibble(
  Male = c(67.91, 63.04, 73.21, 69.59),
  Female = c(65.81, 62.30, 73.63, 69.02),
  Category = factor(c("Knowledge", "Attitude", "Behavior", "Total Score"), levels = c("Knowledge", "Attitude", "Behavior", "Total Score"))
) -> xdf_gender

xdf_gender2 <- gather(xdf_gender, group, value, !Category)
xdf_gender2

db_plot_gender <- ggplot(xdf_gender, aes(y = Category)) + 
  geom_dumbbell(aes(x = Female, xend = Male), size=3, color="darkgrey", size_x=5, size_xend=5) +
  geom_point(data = xdf_gender2, aes(x = value, color = group), size = 5) +
  theme_classic() +
  scale_color_manual(name = "Gender", values = c("red", "blue") ) +
  labs(x="Score", 
       y=element_blank()) +
  theme(legend.position = "top") +
  scale_x_continuous(#breaks=seq(5,13,1), 
    limits = c(60,80))

#dataset for academic role

tibble(
  Student = c(65.0, 61.17, 72.77, 68.15),
  Faculty = c(71.91, 70.15, 75.15, 73.18),
  Staff = c(70.48, 63.56, 74.71, 71.21),
  Category = factor(c("Knowledge", "Attitude", "Behavior", "Total Score"), levels = c("Knowledge", "Attitude", "Behavior", "Total Score"))
) -> xdf_role

xdf_role2 <- gather(xdf_role, group, value, !Category)

db_plot_role <- ggplot(xdf_role, aes(y = Category)) +
  geom_dumbbell(aes(x = Student, xend = Faculty), size=3, color="darkgrey", size_x=5, size_xend=5) +
  geom_point(data = xdf_role2, aes(x = value, color = group), size = 5) +
  theme_classic() +
  scale_color_manual(name = "Academic Role", values = c("#064635", "#519259", "#F0BB62") ) +
  labs(x="Score", 
       y=element_blank()) +
  theme(legend.position = "top") +
  scale_x_continuous(
    limits = c(60,80)) +
  rremove("y.text")

#combine two plots

fig3 <- ggarrange(db_plot_gender, db_plot_role) #combine plots
fig3 <- annotate_figure(fig3,
                top = text_grob("SSO Account Security Awareness by Gender and Academic Role", face = "bold", size = 14)) #add text in the middle
fig3

ggsave("fig3.pdf", plot= fig3, dpi="print")
```

## OLS Regression
### Model 1: Privacy
```{r}
model1 <- lm(score ~ gender + age + roles + familiarity + privacy, data = data)
summary(model1)
```
### Model 2: Privacy + Big5
```{r}
model2 <- lm(score ~ gender + age + roles + familiarity + privacy + extraversion + agreeableness + conscientiousness + emotionalstability + openness, data = data)
summary(model2)
```
### Model 3: Privacy x Big5
```{r}
model3 <- lm(score ~ gender + age + roles + familiarity + privacy + extraversion + agreeableness*privacy + conscientiousness*privacy + emotionalstability + openness, data = data)
summary(model3)
```
## Diagnostics
### Residuals vs Fitted
```{r}
plot(model1, 1)
plot(model2, 1)
plot(model3, 1)
```
### Normal Q-Q
```{r}
plot(model1, 2)
plot(model2, 2)
plot(model3, 2)
```
### Scale-Location
```{r}
plot(model1, 3)
plot(model2, 3)
plot(model3, 3)
```
### Cook's distance
```{r}
plot(model1, 4)
plot(model2, 4)
plot(model3, 4)
```

### Residuals vs Leverage
```{r}
plot(model1, 5)
plot(model2, 5)
plot(model3, 5)
```
### Other Approaches
```{r}
library("car")
qqPlot(model1,labels=row.names(id), id.method="identify", simulate=TRUE, main="Q-Q Plot")
qqPlot(model2,labels=row.names(id), id.method="identify", simulate=TRUE, main="Q-Q Plot")
qqPlot(model3,labels=row.names(id), id.method="identify", simulate=TRUE, main="Q-Q Plot")
outlierTest(model1)
outlierTest(model2)
outlierTest(model3)
```
```{r}
influencePlot(model1, main="Influence Plot", sub="Circle size is proportional to Cook’s distance")
influencePlot(model2, main="Influence Plot", sub="Circle size is proportional to Cook’s distance")
influencePlot(model3, main="Influence Plot", sub="Circle size is proportional to Cook’s distance")
```
```{r}
qqPlot(model1,labels=row.names(id), id.method="identify", simulate=TRUE, main="Q-Q Plot")

highleverage <- function(fit) {
 p <- length(coefficients(fit))
 n <- length(fitted(fit))
 ratio <-p/n
 plot(hatvalues(fit), main="Index Plot of Ratio")
 abline(h=c(2,3)*ratio, col="red", lty=2)
 text(hatvalues(fit), labels=rownames(data), font = 2)
}
highleverage(model1)

influencePlot(model1, main="Influence Plot", sub="Circle size is proportional to Cook’s distance")
```
```{r}
qqPlot(model2,labels=row.names(id), id.method="identify", simulate=TRUE, main="Q-Q Plot")

highleverage <- function(fit) {
 p <- length(coefficients(fit))
 n <- length(fitted(fit))
 ratio <-p/n
 plot(hatvalues(fit), main="Index Plot of Ratio")
 abline(h=c(2,3)*ratio, col="red", lty=2)
 text(hatvalues(fit), labels=rownames(data), font = 2)
}
highleverage(model2)

influencePlot(model2, main="Influence Plot", sub="Circle size is proportional to Cook’s distance")
```


```{r}
qqPlot(model3,labels=row.names(id), id.method="identify", simulate=TRUE, main="Q-Q Plot")

highleverage <- function(fit) {
 p <- length(coefficients(fit))
 n <- length(fitted(fit))
 ratio <-p/n
 plot(hatvalues(fit), main="Index Plot of Ratio")
 abline(h=c(2,3)*ratio, col="red", lty=2)
 text(hatvalues(fit), labels=rownames(data), font = 2)
}
highleverage(model3)

influencePlot(model3, main="Influence Plot", sub="Circle size is proportional to Cook’s distance")
```
## Without Outliers, High-Leverage, & Influential Cases
```{r}
data2 <- data[-c(101, 252, 169),]
summary(data2)
```
### Model 01: Demographics Only
```{r}
model0b <- lm(score ~ gender + age + roles, data = data2)
summary(model0b)
```
### Model 02: Familiarity
```{r}
model0c <- lm(score ~ gender + age + roles + familiarity, data = data2)
summary(model0c)
```
### Model 1b: Privacy
```{r}
model1b <- lm(score ~ gender + age + roles + familiarity + privacy, data = data2)
summary(model1b)
lm.beta(model1b)
```

### Model 2b: Privacy + Big5
```{r}
model2b <- lm(score ~ gender + age + roles + familiarity + privacy + extraversion + agreeableness + conscientiousness + emotionalstability + openness, data = data2)
summary(model2b)
lm.beta(model2b)
```
### Model 3b: Privacy x Big5
```{r}
model3b <- lm(score ~ gender + age + roles + familiarity + privacy + extraversion + agreeableness*privacy + conscientiousness*privacy + emotionalstability + openness, data = data2)
summary(model3b)
lm.beta(model3b)
```
## Model Comparison
### Model 1b vs Model 2b
```{r}
anova(model1b, model2b)
anova(model1b, model2b, test="Chisq")
```
### Model 2b vs Model 3b
```{r}
anova(model2b, model3b)
anova(model2b, model3b, test="Chisq")
```
## Regression Visualization
### Marginal Effects Plot
```{r}
plot1 <- plot_model(model3b, type = "pred", terms = c("privacy", "agreeableness[1,3,5,7]"), title = "", axis.title = c("Privacy Concerns", "Predicted Security Awareness Score"), legend.title = "Agreeableness", colors = "PRGn") + ylim(0, 100)
plot2 <- plot_model(model3b, type = "pred", terms = c("privacy", "conscientiousness[1,3,5,7]"), title = "", axis.title = c("Privacy Concerns", "Predicted Security Awareness Score"), legend.title = "Conscientiousness", colors = "PRGn")+ ylim(0, 100)
#plot1
#plot2
fig4 <- grid.arrange(plot1, plot2, ncol=2,top=text_grob("Marginal Effects on SSO Security Awareness Score"))
ggsave("fig4.pdf", plot= fig4, dpi="print")
```